A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-10-29 paper/main.tex
Use correct funding statement

\subsection*{Grant information}
COH was supported by a graduate stipend from the German federal state of
Saxony-Anhalt and MH was supported by funds from the German federal state of
Saxony-Anhalt and the European Regional Development Fund (ERDF), Project:
Center for Behavioral Brain Sciences (CBBS). Work on the adapting data
management technology for this study was in part supported by the European
Union's Horizon 2020 Research and Innovation Programme under Grant Agreement
no. 785907 (HBP SGA2).

>>>>

\subsection*{Grant information}

COH was supported by a graduate stipend from the German federal state of
Saxony-Anhalt and MH was, in-part, supported by funds from the German federal
state of Saxony-Anhalt and the European Regional Development Fund (ERDF),
Project: Center for Behavioral Brain Sciences (CBBS). Development of the data
management technology used to publish these data on the OpenScienceFramework
was co-funded by the US National Science Foundation (NSF 1912266), and the
German Federal Ministry of Education and Research (BMBF 01GQ1905).
